---
title: "Stats Midterm Generator"
format: html
editor: visual
---

```{r, echo = FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

# Code for Generators

```{r}
set.seed(1)
```

```{r}
# midterm = 0.20
# parts = c(
#   original = 0.50,
#   study_materials = 0.20,
#   corrections_and_reflections = 0.20,
#   retake = 0.10
# )
# parts*midterm
```

```{r message = FALSE, warning = FALSE}
library(MCMCpack)
library(tidyverse)

siground = function(x, sig_figs) {
  digits = floor(log10(x))
  round(x*10^(-digits), sig_figs - 1)*10^digits
}

percent = function(x) {
  str_c(x*100, "%")
}
```

```{r}
possible_story_structures = c(
  "proportion",
  "difference of proportions",
  "mean",
  "difference of means",
  "mean difference",
  "slope",
  "chisquared"
)
```

## Inference for a proportion

```{r}
proportion_stories = list(
  # "" = list(
  #   "procedure" = sample(c("test", "interval"), ),
  #   "p0" = c("lower" = , "upper" = , "sigfigs" = ),
  #   "p" = c("lower" = , "upper" = , "sigfigs" = ),
  #   "sampling_methods" = c("random"),
  #   "n_params" = c("lower" = , "upper" = , "sigfigs" = ),
  #   "direction" = sample(c("higher", "lower", "different")),
  #   "text" = function(params) {
  #     sampling_method = params[["sampling_method"]]
  #     if (sampling_method == "") {
  #       sampling_text = str_c()
  #     }
  #     if (params[["procedure"]] == "interval") {
  #       question = str_c()
  #     } else {
  #       question = str_c()
  #     }
  #     str_c(
  #     )
  #   }
  # ),
  "water" = list(
    "procedure" = "test",
    "p0" = c("lower" = 1/3, "upper" = 1/3, "sigfigs" = 10),
    "p" = c("lower" = 1/3, "upper" = 0.8, "sigfigs" = 2),
    "sampling_methods" = c("census", "census"),
    "n_params" = c("lower" = 10, "upper" = 40, "sigfigs" = 2),
    "direction" = "higher",
    "text" = function(params) {
      sampling_method = params[["sampling_method"]]
      if (sampling_method == "") {
        sampling_text = str_c()
      }
      str_c(
        "A class did a study to see if students in the class could taste water and identify bottled water versus tap water. Each student was presented with three cups of water --- one of which contained bottled water --- and they were directed to identify which cup they thought contained bottled water. The class wants to test (at a significance level of ", params[["alpha"]], ") if they correctly identified the bottled water significantly better than they would have done by simply guessing. There are ", params[["n"]],
        " students in the class, and ", params[["x"]], " of them correctly identified the bottled water."
      )
    }
  ),
  "lighbulbs" = list(
    "procedure" = sample(c("test", "interval"), 1),
    "p0" = c("lower" = 0.01, "upper" = 0.1, "sigfigs" = 1),
    "p" = c("lower" = 0.01, "upper" = 0.1, "sigfigs" = 1),
    "sampling_methods" = c("cluster", "random", "systematic"),
    "n_params" = c("lower" = 20, "upper" = 100, "sigfigs" = 1),
    "direction" = "higher",
    "text" = function(params) {
      sampling_method = params[["sampling_method"]]
      if (sampling_method == "cluster") {
        sampling_text = str_c(
          "Leandro randomly samples 5 boxes (each containing ",
          params[["n"]] / 5, 
          " lightbulbs) and combines them to form a sample of ",
          params[["n"]],
          " lightbulbs."
        )
      } else if (sampling_method == "random") {
        sampling_text = str_c(
          "Leandro takes a random sample of ",
          params[["n"]],
          " bulbs."
        )
      } else if (sampling_method == "systematic") {
        sampling_text = str_c(
          "Leandro randomly samples a number between 1 and 100 for the first bulb, then samples every 10th bulb shipped to his store until he has collected a sample of ",
          params[["n"]],
          " bulbs."
        )
      }
      if (params[["procedure"]] == "interval") {
        question = str_c(
          "Leandro wants to estimate (at a ",
          params[["confidence_level"]],
          "% confidence level) the proportion of light bulbs that arrive broken upon shipment to his store.")
      } else {
        question = str_c(
          "Leandro thinks proportion of light bulbs that arrive broken upon shipment to his store might be higher than ",
          params[["p0"]],
          ".")
      }
      str_c(
        question,
        " His store is large, and recieves thousands of lightbulbs each week. ",
        sampling_text,
        " He finds that ",
        params[["x"]],
        " arrived broken."
      )
    }
  ),
  "approval_rating" = list(
    "procedure" = "test",
    "sampling_methods" = c("random", "convenience", "wording_bias"),
    "p0" = c("lower" = 0.2, "upper" = 0.7, "sigfigs" = 1),
    "p" = c("lower" = 0.2, "upper" = 0.7, "sigfigs" = 1),
    "n_params" = c("lower" = 300, "upper" = 2000, "sigfigs" = 2),
    "direction" = sample(c("lower", "different", "higher"), 1),
    "text" = function(params) {
      sampling_method = params[["sampling_method"]]
      if (sampling_method == "convenience") {
        sampling_text = str_c(
          "She creates a poll on Twitter and invites adults in that nation to share how they feel about the prime minister. ",
          params[["n"]],
          " people respond to her poll."
        )
      } else if (sampling_method == "random") {
        sampling_text = str_c(
          "she takes a random sample of ",
          params[["n"]],
          " adults in that nation"
        )
      } else if (sampling_method == "wording_bias") {
        sampling_text = str_c(
          "She calls a random sample of ",
          params[["n"]],
          " registered voters in that nation and asks the question, 'Do you agree with the large percent of people who approve of the prime minister?'."
        )
      }
      str_c(
        "A large poll showed that ",
        percent(params[["p0"]]),
        " of adults approved of their nation's prime minister. Margot wants to test (at a significance level of α=",
        params[["alpha"]],
        ") if it is now ",
        params[["direction"]], #lower, different, higher
        ". ",
        sampling_text,
        " She finds that ",
        params[["x"]],
        " --- or ",
        percent(params[["phat"]]),
        " of those sampled --- approved of the prime minister."
      )
    }
  )
)
```

```{r}
generate_proportion_story = function(story) {
procedure = story[["procedure"]]

n_params = story[["n_params"]]
n = siground(
  runif(1, n_params[["lower"]], n_params[["upper"]]),
  n_params[["sigfigs"]]
)
if (procedure == "test") {
  p0_params = story[["p0"]]
  p0 = siground(runif(1, p0_params[["lower"]], p0_params[["upper"]]),
                p0_params[["sigfigs"]])
  direction = story[["direction"]]
  
  if (sample(1:2, 1) == 1) {
    p_params = story[["p"]]
    if (direction == "lower") {
      p = siground(
        runif(1, p_params[["lower"]], p0),
              p_params[["sigfigs"]]
        ) 
    } else if (direction == "upper") {
      p = siground(
        runif(1, p0, p_params[["upper"]]),
        p_params[["sigfigs"]]
      ) 
    } else {
      p = siground(
        runif(1, p_params[["lower"]], p_params[["upper"]]),
        p_params[["sigfigs"]]
      ) 
    }
  } else {
    p = p0
  }
  sample_x = function() {
    x = siground(rbinom(1, n, p), 2)
    phat = x/n
    if (direction == "lower") {
      if (phat < p0) {
        return(x)
      } else {
        return(sample_x())
      }
    } else if (direction == "higher") {
      if (phat > p0) {
        return(x)
      } else {
        return(sample_x())
      }
    } else {
      if (phat == p) {
        return(sample_x())
      } else {
        return(x)
      }
    }
  }
  x = sample_x()
  phat = siground(x / n, 2)
} else {
  p_params = story[["p"]]
  p = siground(runif(1, p_params[["lower"]], p_params[["upper"]]), p_params[["sigfigs"]])
}

confidence_level = sample(c(80, 85, 90, 95, 99), 1)
alpha = 1 - confidence_level/100

sampling_method = sample(story[["sampling_methods"]], 1)

story[["text"]](
  list(
    "p0" = p0,
    "n" = n,
    "phat" = phat,
    "procedure" = procedure,
    "direction" = direction,
    "x" = x,
    "sampling_method" = sampling_method,
    "alpha" = alpha,
    "confidence_level" = confidence_level
  )
)
}
```

## Inference for a mean

```{r}
mean_stories = list()
generate_mean_story = function (story) {}
```

## Inference for a slope

```{r}
slope_stories = list()
generate_slope_story = function (story) {}
```

## Inference for a difference of proportions

```{r}
diffprop_stories = list()
generate_diffprop_story = function (story) {}
```

## Inference for a differene of means

```{r}
diffmean_stories = list()
generate_diffmean_story = function (story) {}
```

## Inference for a mean difference

```{r}
meandiff_stories = list()
generate_meandiff_story = function (story) {}
```

## Chi-squared

```{r}
chisquared_stories = list()
generate_chisquared_story = function (story) {}
```

# Random Quiz Question

```{r}
story_structure = sample(possible_story_structures, 1)
if (story_structure == "proportion") {
  story = sample(proportion_stories, 1)[[1]]
  story_text = generate_proportion_story(story)
} else if (story_structure == "mean") {
  story = sample(mean_stories, 1)[[1]]
  story_text = generate_mean_story(story)
} else if (story_structure == "slope") {
  story = sample(slope_stories, 1)[[1]]
  story_text = generate_slope_story(story)
} else if (story_structure == "difference of proportions") {
  story = sample(diffprop_stories, 1)[[1]]
  story_text = generate_diffprop_story(story)
} else if (story_structure == "difference of means") {
  story = sample(diffmean_stories, 1)[[1]]
  story_text = generate_diffmean_story(story)
} else if (story_structure == "mean difference") {
  story = sample(meandiff_stories, 1)[[1]]
  story_text = generate_meandiff_story(story)
} else if (story_structure == "chisquared") {
  story = sample(chisquared_stories, 1)[[1]]
  story_text = generate_chisquared_story(story)
}
```

`r story_text`

## Part 1: Identify the study design

The individuals in this study are: 

How many variables are there and what is/are the variable type(s)?
(Check one box and fill out the question below it.)

* [ ] There is one variable in the study.
    * Variable _________ is (categorical / quantitative)
* [ ] There are two variables in the study.
    * Variable _________ is (categorical / quantitative)
    * Variable _________ is (categorical / quantitative)

The sample is: __________

The population of interest is: ________

What statistical analysis could you use to address the research question? _____________

## Part 2: Represent the data

Draw an appropriate graph of the sample data.

`r if (story_structure %in% c("mean", "difference of means", "mean difference")) {"Describe the distribution."}`
`r if (story_structure %in% c("slope")) {"Describe the relationship."}`

## Part 3: Critique the study design

Are the conditions for the appropriate statistical inference procedure met? If NOT, what improvements could you make to the study design?

## Part 4: Do the statistical analysis

Assume that the conditions are met (even if you showed in the previous section that they are not).

State your conclusion in context, assuming conditions are met and the study design is good.

## Part 5: How much do you trust the conclusion, given the actual study design?






```{r}
# set.seed(1)
# n_vars = sample(c(1, 2), 1)
# var_type = sample(c("categorical", "quantitative"), 1)
# if (n_vars == 1) {
#   if (var_type == "categorical") {
#     n_groups = sample(1:5, 1)
#   }
#   n_groups = sample(c(1, 2), 1)
# } else {
#   n_groups = 1
# }
# data_type = str_c(n_vars, " variable ", var_type, " data (", n_groups, " group)")
# data_type
# if (data_type == "1 variable quantitative data (1 group)") {
#   print("1 var quant (1)")
#   mu = 1 #TODO
#   sigma = #TODO
#   mu0 = 1 #TODO
#   n = 10 #TODO
#   distribution_type = rnorm #TODO
#   x = distribution_type(n, mu, sigma)
#   print(x)
# } else if (data_type == "1 variable categorical data (1 group)") {
#   print("1 var cat (1)")
#   ncats = sample(2:6, 1)
#   concentrations = rep(1, ncats) #TODO
#   probs = rdirichlet(1, concentrations)
#   probs0 = c(rep(1, ncats)) #TODO
#   n = 10 #TODO
#   x = rmultinom(1, n, probs)
#   print(x)
# }  else if (data_type == "1 variable categorical data (2 group)") {
#   print("1 var cat (2)")
#   ncats = 2#sample(2:6, 1)
#   concentrations = rep(1, ncats) #TODO
#   probs1 = rdirichlet(1, concentrations)
#   probs2 = rdirichlet(1, concentrations)
#   # probs0 = c(rep(1, ncats)) #TODO
#   n1 = 10 #TODO
#   n2 = 10 #TODO
#   x1 = rmultinom(1, n1, probs1) #TODO
#   x2 = rmultinom(1, n2, probs1) #TODO
#   print(x1)
#   print(x2)
# }else if (data_type == "1 variable quantitative data (2 group)") {
#   print("1 var quant (2)")
#   mu1 = 1 #TODO
#   mu2 = 1 #TODO
#   sigma1 = 1 #TODO
#   sigma2 = 1 #TODO
#   n1 = 10 #TODO
#   n2 = 10 #TODO
#   distribution_type = rnorm #TODO
#   x1 = distribution_type(n1, mu1, sigma1)
#   print(x1)
#   x2 = distribution_type(n2, mu2, sigma2)
#   print(x2)
# } else if (data_type == "2 variable categorical data (1 group)") {
#   
# }

```

```{r}
# sample_data_type = function(i = NA, allow_chisq = FALSE) {
#   var_type =
#     sample(
#       c("categorical", "quantitative"),
#       1,
#       prob = c(1, 2)
#     )
#   if (allow_chisq || var_type == "quantitative") {
#     n_vars = sample(c(1,2), 1, prob = c(2, 1))
#   } else {
#     n_vars = 1
#   }
#   if (n_vars == 1) {
#     if (var_type == "categorical") {
#       if (allow_chisq) {
#         n_groups = sample(1:5, 1, prob = c(5, 5, 1, 1, 1))
#       } else {
#         n_groups = sample(1:2, 1)
#       }
#     } else if (var_type == "quantitative") {
#       n_groups = sample(1:2, 1)
#     }
#   } else {
#     n_groups = 1
#   }
#   data_type =
#     str_c(
#       n_vars,
#       " variable ",
#       var_type,
#       " data (",
#       n_groups,
#       " group)"
#     )
#   data_type
# }
```

```{r}
# ggplot(NULL, aes(x = sapply(1:10000, sample_data_type, allow_chisq = TRUE))) +
#   geom_bar() +
#   coord_flip()
```
