---
title: "Stats Midterm Generator"
format: docx
editor: visual
---

```{r, echo = FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

# Code for Generators

```{r}
# midterm = 0.20
# parts = c(
#   original = 0.50,
#   study_materials = 0.20,
#   corrections_and_reflections = 0.20,
#   retake = 0.10
# )
# parts*midterm
```

```{r message = FALSE, warning = FALSE}
library(MCMCpack)
library(tidyverse)

siground = function(x, sig_figs) {
  if (x == 0) {
    return(0)
  } else if (x > 0) {
  digits = floor(log10(x))
  round(x*10^(-digits), sig_figs - 1)*10^digits
  } else if (x < 0) {
  digits = floor(log10(-x))
  round(x*10^(-digits), sig_figs - 1)*10^digits
  }
}

percent = function(x) {
  str_c(x*100, "%")
}

sample_from_range = function(params) {
  siground(
    runif(1, params[["lower"]], params[["upper"]]),
    params[["sigfigs"]]
  )
}


sample_x = function(sampling_function, direction, label, h0) {
  x = sampling_function()
  if (direction == "lower") {
    if (x[[label]] < h0) {
      return(x)
    } else {
      return(sample_x(sampling_function, direction, label, h0))
    }
  } else if (direction == "higher") {
    if (x[[label]] > h0) {
      return(x)
    } else {
      return(sample_x(sampling_function, direction, label, h0))
    }
  } else {
    if (x[[label]] == h0) {
      return(sample_x(sampling_function, direction, label, h0))
    } else {
      return(x)
    }
  }
}
```

## Question Types

```{r}
possible_story_structures = c(
  "proportion",
  #"difference of proportions",
  "mean",
  #"difference of means",
  #"mean difference",
  "slope"#,
  #"chisquared"
)
```

## Proportion

```{r}
proportion_stories = list(
  # "" = list(
  #   "procedure" = sample(c("test", "interval"), ),
  #   "p0" = c("lower" = , "upper" = , "sigfigs" = ),
  #   "p" = c("lower" = , "upper" = , "sigfigs" = ),
  #   "sampling_methods" = c("random"),
  #   "n_params" = c("lower" = , "upper" = , "sigfigs" = ),
  #   "direction" = sample(c("higher", "lower", "different")),
  #   "text" = function(params) {
  #     sampling_method = params[["sampling_method"]]
  #     if (sampling_method == "") {
  #       sampling_text = str_c()
  #     }
  #     if (params[["procedure"]] == "interval") {
  #       question = str_c()
  #     } else {
  #       question = str_c()
  #     }
  #     str_c(
  #     )
  #   }
  # ),
  "water" = list(
    "procedure" = "test",
    "p0" = c("lower" = 1/3, "upper" = 1/3, "sigfigs" = 10),
    "p" = c("lower" = 1/3, "upper" = 0.8, "sigfigs" = 2),
    "sampling_methods" = c("census", "census"),
    "n_params" = c("lower" = 10, "upper" = 40, "sigfigs" = 2),
    "direction" = "higher",
    "text" = function(params) {
      sampling_method = params[["sampling_method"]]
      if (sampling_method == "") {
        sampling_text = str_c()
      }
      str_c(
        "A class did a study to see if students in the class could taste water and identify bottled water versus tap water. Each student was presented with three cups of water --- one of which contained bottled water --- and they were directed to identify which cup they thought contained bottled water. The class wants to test (at a significance level of ", params[["alpha"]], ") if they correctly identified the bottled water significantly better than they would have done by simply guessing. There are ", params[["n"]],
        " students in the class, and ", params[["x"]], " of them correctly identified the bottled water."
      )
    }
  ),
  "lighbulbs" = list(
    "procedure" = sample(c("test", "interval"), 1),
    "p0" = c("lower" = 0.01, "upper" = 0.1, "sigfigs" = 1),
    "p" = c("lower" = 0.01, "upper" = 0.1, "sigfigs" = 1),
    "sampling_methods" = c("cluster", "random", "systematic"),
    "n_params" = c("lower" = 20, "upper" = 100, "sigfigs" = 1),
    "direction" = "higher",
    "text" = function(params) {
      sampling_method = params[["sampling_method"]]
      if (sampling_method == "cluster") {
        sampling_text = str_c(
          "Leandro randomly samples 5 boxes (each containing ",
          params[["n"]] / 5, 
          " lightbulbs) and combines them to form a sample of ",
          params[["n"]],
          " lightbulbs."
        )
      } else if (sampling_method == "random") {
        sampling_text = str_c(
          "Leandro takes a random sample of ",
          params[["n"]],
          " bulbs."
        )
      } else if (sampling_method == "systematic") {
        sampling_text = str_c(
          "Leandro randomly samples a number between 1 and 100 for the first bulb, then samples every 10th bulb shipped to his store until he has collected a sample of ",
          params[["n"]],
          " bulbs."
        )
      }
      if (params[["procedure"]] == "interval") {
        question = str_c(
          "Leandro wants to estimate (at a ",
          params[["confidence_level"]],
          "% confidence level) the proportion of light bulbs that arrive broken upon shipment to his store.")
      } else {
        question = str_c(
          "Leandro thinks proportion of light bulbs that arrive broken upon shipment to his store might be higher than ",
          params[["p0"]],
          ".")
      }
      str_c(
        question,
        " His store is large, and receives thousands of lightbulbs each week. ",
        sampling_text,
        " He finds that ",
        params[["x"]],
        " arrived broken."
      )
    }
  ),
  "approval_rating" = list(
    "procedure" = "test",
    "sampling_methods" = c("random", "convenience", "wording_bias"),
    "p0" = c("lower" = 0.2, "upper" = 0.7, "sigfigs" = 1),
    "p" = c("lower" = 0.2, "upper" = 0.7, "sigfigs" = 1),
    "n_params" = c("lower" = 300, "upper" = 2000, "sigfigs" = 2),
    "direction" = sample(c("lower", "different", "higher"), 1),
    "text" = function(params) {
      sampling_method = params[["sampling_method"]]
      if (sampling_method == "convenience") {
        sampling_text = str_c(
          "She creates a poll on Twitter and invites adults in that nation to share how they feel about the prime minister. ",
          params[["n"]],
          " people respond to her poll."
        )
      } else if (sampling_method == "random") {
        sampling_text = str_c(
          "she takes a random sample of ",
          params[["n"]],
          " adults in that nation"
        )
      } else if (sampling_method == "wording_bias") {
        sampling_text = str_c(
          "She calls a random sample of ",
          params[["n"]],
          " registered voters in that nation and asks the question, 'Do you agree with the large percent of people who approve of the prime minister?'."
        )
      }
      str_c(
        "A large poll showed that ",
        percent(params[["p0"]]),
        " of adults approved of their nation's prime minister. Margot wants to test (at a significance level of α=",
        params[["alpha"]],
        ") if it is now ",
        params[["direction"]], #lower, different, higher
        ". ",
        sampling_text,
        " She finds that ",
        params[["x"]],
        " --- or ",
        percent(params[["phat"]]),
        " of those sampled --- approved of the prime minister."
      )
    }
  )
)
```

```{r}
generate_proportion_story = function(story) {
procedure = story[["procedure"]]

n = sample_from_range(story[["n_params"]])
p0 = sample_from_range(story[["p0"]])
direction = story[["direction"]]
if (procedure == "test") {
  
  if (sample(1:2, 1) == 1) {
    p_params = story[["p"]]
    if (direction == "lower") {
      p_params[["upper"]] = p0
    } else if (direction == "upper") {
      p_params[["lower"]] = p0
    }
    p = sample_from_range(p_params)
  } else {
    p = p0
  }
  xphat = sample_x(
    sampling_function = function() {
      x = siground(rbinom(1, n, p), 2)
      phat = x/n
      c("x" = x, "phat" = phat)
    },
    direction,
    "phat",
    p0
  )
  x = xphat[["x"]]
} else {
  p = sample_from_range(story[["p"]])
  x = siground(rbinom(1, n, p), 2)
}
phat = siground(x / n, 2)

confidence_level = sample(c(80, 85, 90, 95, 99), 1)
alpha = 1 - confidence_level/100

sampling_method = sample(story[["sampling_methods"]], 1)

list(
  "text" = story[["text"]](
    list(
      "p0" = p0,
      "n" = n,
      "phat" = phat,
      "procedure" = procedure,
      "direction" = direction,
      "x" = x,
      "sampling_method" = sampling_method,
      "alpha" = alpha,
      "confidence_level" = confidence_level
    )
  ),
  "structure" = "proportion"
)
}
```

## Mean

```{r}
mean_stories = list(
  # "" = list(
  #   "procedure" = sample(c("test", "interval"), 1),
  #   "direction" = "higher",
  #   "sampling_methods" = c("random", "convenience"),
  #   "n_params" = c("lower" = , "upper" = , "sigfigs" = ),
  #   "mu0_params" = c("lower" = , "upper" = , "sigfigs" = ),
  #   "mu_params" = c("lower" = , "upper" = , "sigfigs" = ),
  #   "s_params" = c("lower" = , "upper" = , "sigfigs" = ),
  #   "text" = function(params) {
  #     if (params[["procedure"]] == "test") {
  #       question = str_c(
  #       )
  #     } else {
  #       question = str_c(
  #       )
  #     }
  #     if (params[["sampling_method"]] == "random") {
  #       sampling_method = str_c(
  #       )
  #     }
  #     str_c(
  #     )
  #   }
  # ),
  "housing" = list(
    "procedure" = sample(c("test", "interval"), 1),
    "direction" = "higher",
    "sampling_methods" = c("random", "cluster", "stratified"),
    "n_params" = c("lower" = 10, "upper" = 50, "sigfigs" = 2),
    "mu0_params" = c("lower" = 1700, "upper" = 4000, "sigfigs" = 3),
    "mu_params" = c("lower" = 1700, "upper" = 4000, "sigfigs" = 3),
    "s_params" = c("lower" = 100, "upper" = 2000, "sigfigs" = 2),
    "text" = function(params) {
      if (params[["procedure"]] == "test") {
        question = str_c(
          "They plan to use this data to test the hypothesis that the average rent is now ",
          params[["direction"]],
          " than the previous year's average of ",
          params[["mu0"]],
          "."
        )
      } else {
        question = str_c(
          "They plan to use this data to estimate the average rent in the city."
        )
      }
      if (params[["sampling_method"]] == "random") {
        sampling_method = str_c(
          "They take a random sample of ",
          params[["n"]],
          " rental properties."
        )
      } else if (params[["sampling_method"]] == "stratified") {
        sampling_method = str_c(
          "For each of the 5 main neighborhoods in the city, they get a random sample, and combine their data into a single sample of ",
          params[["n"]],
          " rental properties."
        )
      } else if (params[["sampling_method"]] == "cluster") {
        sampling_method = str_c(
          "They randomly sample 5 streets within the city and collect data on every rental property on the sampled streets. They combine the their data into a single sample of ",
          params[["n"]],
          " rental properties."
        )
      } 
      str_c(
        "An economist is curious about the average cost of rent per month in their large city. ",
        sampling_method,
        " The economist finds that those properties have a mean cost of $",
        params[["xbar"]],
        " per month with a standard deviation of about $",
        params[["s"]],
        ". ",
        " The costs of rent per month for each of the ",
        params[["n"]],
        " properties and the 5-number summary of the dataset is shown below. ",
        question
      )
    }
  ),
  "streaming" = list(
    "procedure" = sample(c("test", "interval"), 1),
    "direction" = "higher",
    "sampling_methods" = c("random", "convenience"),
    "n_params" = c("lower" = 10, "upper" = 50, "sigfigs" = 2),
    "mu0_params" = c("lower" = 1, "upper" = 3, "sigfigs" = 2),
    "mu_params" = c("lower" = 1, "upper" = 3, "sigfigs" = 2),
    "s_params" = c("lower" = 0.2, "upper" = 2, "sigfigs" = 2),
    "text" = function(params) {
      if (params[["procedure"]] == "test") {
        question = str_c(
          "know if the average session length was longer than ",
          params[["mu0"]],
          "."
        )
      } else {
        question = str_c(
          "get a new estimate of the average session length."
        )
      }
      if (params[["sampling_method"]] == "random") {
        sampling_method = str_c(
          " They randomly sampled ",
          params[["n"]],
          " users."
        )
      } else if (params[["sampling_method"]] == "convenience") {
        sampling_method = str_c(
          " They measured the session lengths for the first ",
          params[["n"]],
          " users who logged on to the new site."
        )
      }
      str_c(
        "A website streams movies and television shows to its subscribers. Employees know that the average time a user spends per session on their website is usually ",
        params[["mu0"]],
        " hours. But recently, the website changed its design, and they wanted to ",
        question,
        sampling_method,
        " The session lengths of each of these ",
        params[["n"]],
        " users and the 5-number summary of the data are shown below.",
        " Users in the sample had a mean session length of ",
        params[["xbar"]],
        " hours and a standard deviation of ",
        params[["s"]],
        " hours."
      )
    }
  )
)
```

```{r}
generate_mean_story = function (story) {
  procedure = story[["procedure"]]
  
  # sample size
  n = sample_from_range(story[["n_params"]])
  
  direction = story[["direction"]]
  
  # test
  mu0 = sample_from_range(story[["mu0_params"]])
  s = sample_from_range(story[["s_params"]])
  if (procedure == "test") {
    
    if (sample(1:2, 1) == 1) {
      mu_params = story[["mu_params"]]
      if (direction == "lower") {
        mu_params[["upper"]] = mu0
      } else if (direction == "upper") {
        mu_params[["lower"]] = mu0
      }
      mu = sample_from_range(mu_params)
    } else {
      mu = mu0
    }
    x = sample_x(
      sampling_function = function() {
        x = round(rnorm(n, mu, s))
        xbar = round(mean(x), 1)
        list("x" = x, "xbar" = xbar)
      },
      direction,
      "xbar",
      mu0
    )[["x"]]
    xbar = round(mean(x), 1)
  } else {
    mu = sample_from_range(story[["mu_params"]])
    x = round(rnorm(n, mu, s))
    xbar = round(mean(x), 1)
  }
  
  confidence_level = sample(c(80, 85, 90, 95, 99), 1)
  alpha = 1 - confidence_level/100
  
  sampling_method = sample(story[["sampling_methods"]], 1)
  
  df = tibble(x = sort(x))
  summary_table = df %>% 
    summarise(
      min = round(min(x), 1),
      q1 = round(quantile(x, 0.25), 1),
      median = round(median(x), 1),
      q3 = round(quantile(x, 0.25), 1),
      max = round(max(x), 1)
    )
  
  list(
    "text" = story[["text"]](
      list(
        "mu0" = mu0,
        "n" = n,
        "xbar" = xbar,
        "s" = s,
        "procedure" = procedure,
        "direction" = direction,
        "sampling_method" = sampling_method,
        "alpha" = alpha,
        "confidence_level" = confidence_level
      )
    ),
    "data" = df,
    "summary" = summary_table,
    "structure" = "mean"
  )
}
```

## Slope

```{r}
slope_stories = list(
  # "" = list(
  #   "assignment_methods" = c("random"),
  #   "n_params" = c("lower" = , "upper" = , "sigfigs" = ),
  #   "x_params" = c("lower" = , "upper" = , "sigfigs" = ),
  #   "y_params" = c("lower" = , "upper" = , "sigfigs" = ),
  #   "constraints" = "decreasing",
  #   "shape" = sample(c("linear", "quadratic"), 1),#, "exponential", "cubic"), 1),
  #   "sampling_methods" = c("census"),
  #   "text" = function(params) {
  #     sampling_method = params[["sampling_method"]]
  #     if (sampling_method == "census") {
  #     }
  #     assignment_method = params[["assignment_method"]]
  #     if (assignment_method == "random") {
  #     }
  #     str_c(
  #     )
  #   }
  # ),
  # "heat" = list(
  #   "assignment_methods" = c("random"),
  #   "n_params" = c("lower" = , "upper" = , "sigfigs" = ),
  #   "x_params" = c("lower" = , "upper" = , "sigfigs" = ),
  #   "y_params" = c("lower" = , "upper" = , "sigfigs" = ),
  #   "constraints" = "decreasing",
  #   "shape" = sample(c("linear", "quadratic"), 1),#, "exponential", "cubic"), 1),
  #   "sampling_methods" = c("census"),
  #   "text" = function(params) {
  #     sampling_method = params[["sampling_method"]]
  #     if (sampling_method == "census") {
  #       sampling_text = str_c()
  #     }
  #     assignment_method = params[["assignment_method"]]
  #     if (assignment_method == "random") {
  #     }
  #     str_c(
  #       "Cindy wants to predict how much energy she will use to heat her home based on how cold it is outside. The table below shows the mean amount of gas per day (in cubic meters) that Cindy used each month and the average temperature that month (in degrees Celsius) for one heating season."
  #     )
  #   }
  # ),
  "tomatoes" = list(
    "assignment_methods" = c("random", "confound"),
    "n_params" = c("lower" = 5, "upper" = 12, "sigfigs" = 2),
    "x_params" = c("lower" = 0, "upper" = 8, "sigfigs" = 1),
    "y_params" = c("lower" = 0, "upper" = 12, "sigfigs" = 3),
    "constraints" = "increasing",
    "shape" = sample(c("linear", "quadratic"), 1),#, "exponential", "cubic"), 1),
    "sampling_methods" = c("census", "convenience"),
    "text" = function(params) {
      sampling_method = params[["sampling_method"]]
      if (sampling_method == "census") {
        sampling_text = str_c("Cheryl is curious how different amounts of artificial sunlight will impact the growth of her tomatoes.")
      } else if (sampling_method == "convenience") {
        sampling_text = str_c("Cheryl is curious how different amounts of artificial sunlight could impact the growth of tomato plants.")
      }
      assignment_method = params[["assignment_method"]]
      if (assignment_method == "random") {
        assignment_text = str_c(
          "For each tomato plant, she uses a random number generator to randomly choose how long to leave the grow light on for that plant."
        )
      } else if (assignment_method == "confound") {
        assignment_text = str_c(
          "She arranges the pots aesthetically from smallest (on the left) to largest (on the right) under the grow lights. Then she programs the grow lights so that the left-most plants get the least sunlight and the right-most plants get the most sunlight."
        )
      }
      str_c(
        sampling_text,
        " She has ",
        params[["n"]],
        " potted tomato plants that she keeps in her home and several grow lights that work on a timer. She uses the grow lights to expose her different tomato plants to different amounts of sunlight (in hours per day). ",
        assignment_text,
        " She recorded the change in circumference of each tomato (in centimeters) after a week and calculated the total increase in circumference for each potted plant. Then she ran a linear regression on the data. Her data and the results of her linear regression are summarized in the tables below."
      )
    }
  )
)
generate_slope_story = function (story) {
  assignment_method = sample(story[["assignment_methods"]], 1)
  sampling_method = sample(story[["sampling_methods"]], 1)
  n = round(sample_from_range(story[["n_params"]]))
  x_params = story[["x_params"]]
  y_params = story[["y_params"]]
  x = sapply(seq(x_params[["lower"]], x_params[["upper"]], length.out = n), siground, x_params[["sigfigs"]])
  shape = story[["shape"]]
  rise = (y_params[["upper"]] - y_params[["lower"]])
  run = (x_params[["upper"]] - x_params[["lower"]])
  constraints = story[["constraints"]]
  if (shape == "linear") {
    buffer = 2
    # 3 standard deviations within the range from top to bottom
    # should be about the top and bottom of the linear regression line
    # there should be at least one standard deviation of change within
    # that range, so the max sigma should be rise / 7.
    # the smallest sigma should have a barely visible range,
    # so 3*smallest_sigma >= rise*(smallest visible percent)
    # i can see about 20 divisions easily in a small graph, so let's say
    # smallest sigma is 0.05/3 or about 0.01
    sigma_eps = runif(1, min = rise*0.01, max = rise/(buffer*2+1))
    if (constraints == "increasing") {
      direction = 1 
    } else {
      direction = sample(c(-1, 1, 0), 1)
    }
    # go 3 sigma within the y range above and below to get the y
    # range of the regression line
    beta1 = direction*(rise - 2*buffer*sigma_eps) / run
    if (direction == 0) {
      # 3 sigma above and below the line means for flat line, sigma
      # is about rise / 6
      sigma_eps = rise / (2*buffer)
      # and for flat line, middle of y range is the intercept
      beta0 = rise / 2 + y_params[["lower"]]
    } else if (direction > 0) {
      # if positive, top of graph should be 3 sigma down from
      # ymax, and reached when xmax.
      pred_y_max = y_params[["upper"]] - sigma_eps*buffer
      pred_x_max = x_params[["upper"]]
    } else if (direction < 0) {
      # if negative, top of graph is the same, but reached when
      # xmin
      pred_y_max = y_params[["upper"]] - sigma_eps*buffer
      pred_x_max = x_params[["lower"]]
    }
    beta0 = pred_y_max - beta1 * pred_x_max
    
    error = rnorm(n, mean = 0, sd = sigma_eps)
    y = sapply(beta0 + beta1 * x + error, siground, y_params[["sigfigs"]])
    plot(x,y)
  } else if (shape == "quadratic") {
    buffer = 2
    sigma_eps = runif(1, min = rise*0.01, max = rise/(buffer*2+1))
    
    xmin = x_params[["lower"]]
    xmax = x_params[["upper"]]
    ymin = y_params[["lower"]] + buffer*sigma_eps
    ymax = y_params[["upper"]] - buffer*sigma_eps
    
    error = rnorm(n, mean = 0, sd = sigma_eps)
    # first, sample if we are concave up or down
    a = sample(c(-1, 1), 1)
    if (constraints == "increasing") {
      print("increasing")
      print(str_c("a direction: ", a))
      if (a > 0) {
        # if concave up and increasing, vertex is below xmin
        h = runif(
          1,
          min = xmin - (xmax - xmin)/2,
          max = xmin
        )
      } else {
        # if concave down and increasing, vertex is above xmax
        h = runif(
          1,
          min = xmax,
          max = xmax + (xmax - xmin)/2
        )
      }
      # if increasing, then f(xmin) = ymin and f(xmax) = ymax
      a = a*(ymax - ymin) / ((xmax - h)^2 - (xmin-h)^2)
      k = ymax - a*(xmax - h)^2
    } else if (constraints == "decreasing") {
      if (a > 0) {
        # if concave up and decreasing, vertex is above xmax
        h = runif(
          1,
          min = xmax,
          max = xmax + (xmax - xmin)/2
        )
      } else {
        # if concave down and decreasing, vertex is below xmin
        h = runif(
          1,
          min = xmin - (xmax - xmin)/2,
          max = xmin
        )
      }
      # if decreasing, then f(xmin) = ymax and f(xmax) = ymin
      a = a*(ymax - ymin) / ((xmax - h)^2 - (xmin-h)^2)
      k = ymax - a*(xmin - h)^2
    } else {
        h = runif(
          1,
          min = xmin - (xmax - xmin)/2,
          max = xmax + (xmax - xmin)/2
        )
        if (a > 0) {
          # concave up
          # possible minima are at x=xmin, x=xmax, and x=h
          if (h < xmin) {
            # vertex is to the left, so increasing function
            a = a*(ymax - ymin) / ((xmax - h)^2 - (xmin-h)^2)
            k = ymax - a*(xmax - h)^2
          } else if (x > xmax) {
            # vertex is to the right, so decreasing function
            a = a*(ymax - ymin) / ((xmax - h)^2 - (xmin-h)^2)
            k = ymax - a*(xmin - h)^2
          } else {
            # vertex is (h, ymin)
            k = ymin
            if (h < (xmin - xmax) / 2 + xmin) {
              # vertex is towards the left side of the graph,
              # so f(xmax) = ymax
              a = (ymax - k) / (xmax - h)^2
            } else {
              # f(xmin) = ymax
              a = (ymax - k) / (xmin - h)^2
            }
          }
        } else {
          # concave down
          # possible maxima are at x=xmin, x=xmax, and x=h
          if (h < xmin) {
            # vertex is to the left, so decreasing function
            a = a*(ymax - ymin) / ((xmax - h)^2 - (xmin-h)^2)
            k = ymax - a*(xmin - h)^2
          } else if (x > xmax) {
            # vertex is to the right, so increasing function
            a = a*(ymax - ymin) / ((xmax - h)^2 - (xmin-h)^2)
            k = ymax - a*(xmax - h)^2
          } else {
            # vertex is (h, ymax)
            k = ymax
            if (h < (xmin - xmax) / 2 + xmin) {
              # vertex is towards the left side of the graph,
              # so f(xmax) = ymin
              a = (ymin - k) / (xmax - h)^2
            } else {
              # f(xmin) = ymin
              a = (ymin - k) / (xmin - h)^2
            }
          }
        }
    }
    print(str_c("a = ", a))
    print(str_c("h = ", h))
    print(str_c("k = ", k))
    y = a*(x - h)^2 + k + error
  } else if (shape == "cubic") {
    y = x
  } else if (shape == "exponential") {
    y = x
  }
  df = tibble(x, y) # x and y
  m = lm(y~x)
  summary_table =
    (m %>% summary())$coefficients %>%
    as_tibble() %>%
    select(Estimate, `Std. Error`) # linear regression results
  list(
    "text" = story[["text"]](
      list(
        "assignment_method" = assignment_method,
        "sampling_method" = sampling_method,
        "n" = n
      )
    ),
    "data" = df,
    "summary" = summary_table,
    "structure" = "slope"
  )
}
```

## Inference for a difference of proportions

```{r}
# diffprop_stories = list()
# generate_diffprop_story = function (story) {}
```

## Inference for a differene of means

```{r}
# diffmean_stories = list()
# generate_diffmean_story = function (story) {}
```

## Inference for a mean difference

```{r}
# meandiff_stories = list()
# generate_meandiff_story = function (story) {}
```

## Chi-squared

```{r}
# chisquared_stories = list()
# generate_chisquared_story = function (story) {}
```

## Generate from seed

```{r}
generate_quiz_question = function(seed) {
set.seed(seed)

story_structure = sample(possible_story_structures, 1)
if (story_structure == "proportion") {
  story = sample(proportion_stories, 1)[[1]]
  story_text = generate_proportion_story(story)
} else if (story_structure == "mean") {
  story = sample(mean_stories, 1)[[1]]
  story_text = generate_mean_story(story)
} else if (story_structure == "slope") {
  story = sample(slope_stories, 1)[[1]]
  story_text = generate_slope_story(story)
# } else if (story_structure == "difference of proportions") {
#   story = sample(diffprop_stories, 1)[[1]]
#   story_text = generate_diffprop_story(story)
# } else if (story_structure == "difference of means") {
#   story = sample(diffmean_stories, 1)[[1]]
#   story_text = generate_diffmean_story(story)
# } else if (story_structure == "mean difference") {
#   story = sample(meandiff_stories, 1)[[1]]
#   story_text = generate_meandiff_story(story)
# } else if (story_structure == "chisquared") {
#   story = sample(chisquared_stories, 1)[[1]]
#   story_text = generate_chisquared_story(story)
}
# story_structure
# story_text[["text"]]
story_text
}
```


# Random Quiz Question

```{r}
story_text = generate_quiz_question(1)
```


`r story_text[["text"]]`

```{r}
if (story_text[["structure"]] == "mean") {
  print(story_text[["data"]] %>% pull(x))
# knitr::kable(story_text[["data"]], label = "Data")
knitr::kable(story_text[["summary"]], label = "5-number summary")
}
```


## Part 1: Identify the study design

The individuals in this study are: 

How many variables are there and what is/are the variable type(s)?
(Check one box and fill out the question below it.)

* [ ] There is one variable in the study.
    * Variable _________ is (categorical / quantitative)
* [ ] There are two variables in the study.
    * Variable _________ is (categorical / quantitative)
    * Variable _________ is (categorical / quantitative)

The sample is: __________

The population of interest is: ________

What statistical analysis could you use to address the research question? _____________

## Part 2: Represent the data

Draw an appropriate graph of the sample data.

`r if (story_text[["structure"]] %in% c("mean", "difference of means", "mean difference")) {"Describe the distribution."}`
`r if (story_text[["structure"]] %in% c("slope")) {"Describe the relationship."}`

## Part 3: Critique the study design

Are the conditions for the appropriate statistical inference procedure met? If NOT, what improvements could you make to the study design?

## Part 4: Do the statistical analysis

Assume that the conditions are met (even if you showed in the previous section that they are not).

State your conclusion in context, assuming conditions are met and the study design is good.

## Part 5: How much do you trust the conclusion, given the actual study design?


# Testing

```{r}
# for (i in 2:30) {
#   print(i)
#   story_text = generate_quiz_question(i)
#   print(story_text[["text"]])
#   if (story_text[["structure"]] == "mean") {
#     hist(story_text[["data"]][[1]], main = str_c(story_text[["structure"]], ", seed=", i))
#     print(story_text[["summary"]])
#   }
#   if (story_text[["structure"]] == "slope") {
#     f = plot(story_text[["data"]], main = str_c("seed=", i))
#     print(f)
#     print(story_text[["summary"]])
#   }
# }
```






```{r}
# set.seed(1)
# n_vars = sample(c(1, 2), 1)
# var_type = sample(c("categorical", "quantitative"), 1)
# if (n_vars == 1) {
#   if (var_type == "categorical") {
#     n_groups = sample(1:5, 1)
#   }
#   n_groups = sample(c(1, 2), 1)
# } else {
#   n_groups = 1
# }
# data_type = str_c(n_vars, " variable ", var_type, " data (", n_groups, " group)")
# data_type
# if (data_type == "1 variable quantitative data (1 group)") {
#   print("1 var quant (1)")
#   mu = 1 #TODO
#   sigma = #TODO
#   mu0 = 1 #TODO
#   n = 10 #TODO
#   distribution_type = rnorm #TODO
#   x = distribution_type(n, mu, sigma)
#   print(x)
# } else if (data_type == "1 variable categorical data (1 group)") {
#   print("1 var cat (1)")
#   ncats = sample(2:6, 1)
#   concentrations = rep(1, ncats) #TODO
#   probs = rdirichlet(1, concentrations)
#   probs0 = c(rep(1, ncats)) #TODO
#   n = 10 #TODO
#   x = rmultinom(1, n, probs)
#   print(x)
# }  else if (data_type == "1 variable categorical data (2 group)") {
#   print("1 var cat (2)")
#   ncats = 2#sample(2:6, 1)
#   concentrations = rep(1, ncats) #TODO
#   probs1 = rdirichlet(1, concentrations)
#   probs2 = rdirichlet(1, concentrations)
#   # probs0 = c(rep(1, ncats)) #TODO
#   n1 = 10 #TODO
#   n2 = 10 #TODO
#   x1 = rmultinom(1, n1, probs1) #TODO
#   x2 = rmultinom(1, n2, probs1) #TODO
#   print(x1)
#   print(x2)
# }else if (data_type == "1 variable quantitative data (2 group)") {
#   print("1 var quant (2)")
#   mu1 = 1 #TODO
#   mu2 = 1 #TODO
#   sigma1 = 1 #TODO
#   sigma2 = 1 #TODO
#   n1 = 10 #TODO
#   n2 = 10 #TODO
#   distribution_type = rnorm #TODO
#   x1 = distribution_type(n1, mu1, sigma1)
#   print(x1)
#   x2 = distribution_type(n2, mu2, sigma2)
#   print(x2)
# } else if (data_type == "2 variable categorical data (1 group)") {
#   
# }

```

```{r}
# sample_data_type = function(i = NA, allow_chisq = FALSE) {
#   var_type =
#     sample(
#       c("categorical", "quantitative"),
#       1,
#       prob = c(1, 2)
#     )
#   if (allow_chisq || var_type == "quantitative") {
#     n_vars = sample(c(1,2), 1, prob = c(2, 1))
#   } else {
#     n_vars = 1
#   }
#   if (n_vars == 1) {
#     if (var_type == "categorical") {
#       if (allow_chisq) {
#         n_groups = sample(1:5, 1, prob = c(5, 5, 1, 1, 1))
#       } else {
#         n_groups = sample(1:2, 1)
#       }
#     } else if (var_type == "quantitative") {
#       n_groups = sample(1:2, 1)
#     }
#   } else {
#     n_groups = 1
#   }
#   data_type =
#     str_c(
#       n_vars,
#       " variable ",
#       var_type,
#       " data (",
#       n_groups,
#       " group)"
#     )
#   data_type
# }
```

```{r}
# ggplot(NULL, aes(x = sapply(1:10000, sample_data_type, allow_chisq = TRUE))) +
#   geom_bar() +
#   coord_flip()
```
