---
title: "Stats Midterm Generator"
format: html
editor: visual
---

```{r, echo = FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

# Code for Generators

```{r}
# midterm = 0.20
# parts = c(
#   original = 0.50,
#   study_materials = 0.20,
#   corrections_and_reflections = 0.20,
#   retake = 0.10
# )
# parts*midterm
```

```{r message = FALSE, warning = FALSE}
library(MCMCpack)
library(tidyverse)

siground = function(x, sig_figs) {
  digits = floor(log10(x))
  round(x*10^(-digits), sig_figs - 1)*10^digits
}

percent = function(x) {
  str_c(x*100, "%")
}

sample_from_range = function(params) {
  siground(
    runif(1, params[["lower"]], params[["upper"]]),
    params[["sigfigs"]]
  )
}


sample_x = function(sampling_function, direction, label, h0) {
  x = sampling_function()
  if (direction == "lower") {
    if (x[[label]] < h0) {
      return(x)
    } else {
      return(sample_x(sampling_function, direction, label, h0))
    }
  } else if (direction == "higher") {
    if (x[[label]] > h0) {
      return(x)
    } else {
      return(sample_x(sampling_function, direction, label, h0))
    }
  } else {
    if (x[[label]] == h0) {
      return(sample_x(sampling_function, direction, label, h0))
    } else {
      return(x)
    }
  }
}
```

```{r}
possible_story_structures = c(
  "proportion",
  "difference of proportions",
  "mean",
  "difference of means",
  "mean difference",
  "slope",
  "chisquared"
)
```

## Proportion

```{r}
proportion_stories = list(
  # "" = list(
  #   "procedure" = sample(c("test", "interval"), ),
  #   "p0" = c("lower" = , "upper" = , "sigfigs" = ),
  #   "p" = c("lower" = , "upper" = , "sigfigs" = ),
  #   "sampling_methods" = c("random"),
  #   "n_params" = c("lower" = , "upper" = , "sigfigs" = ),
  #   "direction" = sample(c("higher", "lower", "different")),
  #   "text" = function(params) {
  #     sampling_method = params[["sampling_method"]]
  #     if (sampling_method == "") {
  #       sampling_text = str_c()
  #     }
  #     if (params[["procedure"]] == "interval") {
  #       question = str_c()
  #     } else {
  #       question = str_c()
  #     }
  #     str_c(
  #     )
  #   }
  # ),
  "water" = list(
    "procedure" = "test",
    "p0" = c("lower" = 1/3, "upper" = 1/3, "sigfigs" = 10),
    "p" = c("lower" = 1/3, "upper" = 0.8, "sigfigs" = 2),
    "sampling_methods" = c("census", "census"),
    "n_params" = c("lower" = 10, "upper" = 40, "sigfigs" = 2),
    "direction" = "higher",
    "text" = function(params) {
      sampling_method = params[["sampling_method"]]
      if (sampling_method == "") {
        sampling_text = str_c()
      }
      str_c(
        "A class did a study to see if students in the class could taste water and identify bottled water versus tap water. Each student was presented with three cups of water --- one of which contained bottled water --- and they were directed to identify which cup they thought contained bottled water. The class wants to test (at a significance level of ", params[["alpha"]], ") if they correctly identified the bottled water significantly better than they would have done by simply guessing. There are ", params[["n"]],
        " students in the class, and ", params[["x"]], " of them correctly identified the bottled water."
      )
    }
  ),
  "lighbulbs" = list(
    "procedure" = sample(c("test", "interval"), 1),
    "p0" = c("lower" = 0.01, "upper" = 0.1, "sigfigs" = 1),
    "p" = c("lower" = 0.01, "upper" = 0.1, "sigfigs" = 1),
    "sampling_methods" = c("cluster", "random", "systematic"),
    "n_params" = c("lower" = 20, "upper" = 100, "sigfigs" = 1),
    "direction" = "higher",
    "text" = function(params) {
      sampling_method = params[["sampling_method"]]
      if (sampling_method == "cluster") {
        sampling_text = str_c(
          "Leandro randomly samples 5 boxes (each containing ",
          params[["n"]] / 5, 
          " lightbulbs) and combines them to form a sample of ",
          params[["n"]],
          " lightbulbs."
        )
      } else if (sampling_method == "random") {
        sampling_text = str_c(
          "Leandro takes a random sample of ",
          params[["n"]],
          " bulbs."
        )
      } else if (sampling_method == "systematic") {
        sampling_text = str_c(
          "Leandro randomly samples a number between 1 and 100 for the first bulb, then samples every 10th bulb shipped to his store until he has collected a sample of ",
          params[["n"]],
          " bulbs."
        )
      }
      if (params[["procedure"]] == "interval") {
        question = str_c(
          "Leandro wants to estimate (at a ",
          params[["confidence_level"]],
          "% confidence level) the proportion of light bulbs that arrive broken upon shipment to his store.")
      } else {
        question = str_c(
          "Leandro thinks proportion of light bulbs that arrive broken upon shipment to his store might be higher than ",
          params[["p0"]],
          ".")
      }
      str_c(
        question,
        " His store is large, and recieves thousands of lightbulbs each week. ",
        sampling_text,
        " He finds that ",
        params[["x"]],
        " arrived broken."
      )
    }
  ),
  "approval_rating" = list(
    "procedure" = "test",
    "sampling_methods" = c("random", "convenience", "wording_bias"),
    "p0" = c("lower" = 0.2, "upper" = 0.7, "sigfigs" = 1),
    "p" = c("lower" = 0.2, "upper" = 0.7, "sigfigs" = 1),
    "n_params" = c("lower" = 300, "upper" = 2000, "sigfigs" = 2),
    "direction" = sample(c("lower", "different", "higher"), 1),
    "text" = function(params) {
      sampling_method = params[["sampling_method"]]
      if (sampling_method == "convenience") {
        sampling_text = str_c(
          "She creates a poll on Twitter and invites adults in that nation to share how they feel about the prime minister. ",
          params[["n"]],
          " people respond to her poll."
        )
      } else if (sampling_method == "random") {
        sampling_text = str_c(
          "she takes a random sample of ",
          params[["n"]],
          " adults in that nation"
        )
      } else if (sampling_method == "wording_bias") {
        sampling_text = str_c(
          "She calls a random sample of ",
          params[["n"]],
          " registered voters in that nation and asks the question, 'Do you agree with the large percent of people who approve of the prime minister?'."
        )
      }
      str_c(
        "A large poll showed that ",
        percent(params[["p0"]]),
        " of adults approved of their nation's prime minister. Margot wants to test (at a significance level of α=",
        params[["alpha"]],
        ") if it is now ",
        params[["direction"]], #lower, different, higher
        ". ",
        sampling_text,
        " She finds that ",
        params[["x"]],
        " --- or ",
        percent(params[["phat"]]),
        " of those sampled --- approved of the prime minister."
      )
    }
  )
)
```

```{r}
generate_proportion_story = function(story) {
procedure = story[["procedure"]]

n = sample_from_range(story[["n_params"]])
if (procedure == "test") {
  p0 = sample_from_range(story[["p0"]])
  direction = story[["direction"]]
  
  if (sample(1:2, 1) == 1) {
    p_params = story[["p"]]
    if (direction == "lower") {
      p_params[["upper"]] = p0
    } else if (direction == "upper") {
      p_params[["lower"]] = p0
    }
    p = sample_from_range(p_params)
  } else {
    p = p0
  }
  xphat = sample_x(
    sampling_function = function() {
      x = siground(rbinom(1, n, p), 2)
      phat = x/n
      c("x" = x, "phat" = phat)
    },
    direction,
    "phat",
    p0
  )
  x = xphat[["x"]]
  phat = siground(x / n, 2)
} else {
  p = sample_from_range(story[["p"]])
}

confidence_level = sample(c(80, 85, 90, 95, 99), 1)
alpha = 1 - confidence_level/100

sampling_method = sample(story[["sampling_methods"]], 1)

list(
  "text" = story[["text"]](
    list(
      "p0" = p0,
      "n" = n,
      "phat" = phat,
      "procedure" = procedure,
      "direction" = direction,
      "x" = x,
      "sampling_method" = sampling_method,
      "alpha" = alpha,
      "confidence_level" = confidence_level
    )
  )
)
}
```

## Mean

```{r}
mean_stories = list(
  # "" = list(
  #   "procedure" = sample(c("test", "interval"), 1),
  #   "direction" = "higher",
  #   "sampling_methods" = c("random", "convenience"),
  #   "n_params" = c("lower" = , "upper" = , "sigfigs" = ),
  #   "mu0_params" = c("lower" = , "upper" = , "sigfigs" = ),
  #   "mu_params" = c("lower" = , "upper" = , "sigfigs" = ),
  #   "s_params" = c("lower" = , "upper" = , "sigfigs" = ),
  #   "text" = function(params) {
  #     if (params[["procedure"]] == "test") {
  #       question = str_c(
  #       )
  #     } else {
  #       question = str_c(
  #       )
  #     }
  #     if (params[["sampling_method"]] == "random") {
  #       sampling_method = str_c(
  #       )
  #     }
  #     str_c(
  #     )
  #   }
  # ),
  "housing" = list(
    "procedure" = sample(c("test", "interval"), 1),
    "direction" = "higher",
    "sampling_methods" = c("random", "cluster", "stratified"),
    "n_params" = c("lower" = 10, "upper" = 50, "sigfigs" = 2),
    "mu0_params" = c("lower" = 1700, "upper" = 4000, "sigfigs" = 3),
    "mu_params" = c("lower" = 1700, "upper" = 4000, "sigfigs" = 3),
    "s_params" = c("lower" = 100, "upper" = 2000, "sigfigs" = 2),
    "text" = function(params) {
      if (params[["procedure"]] == "test") {
        question = str_c(
          "They plan to use this data to test the hypothesis that the average rent is now ",
          params[["direction"]],
          " than the previous year's average of ",
          params[["mu0"]],
          "."
        )
      } else {
        question = str_c(
          "They plan to use this data to estimate the average rent in the city."
        )
      }
      if (params[["sampling_method"]] == "random") {
        sampling_method = str_c(
          "They take a random sample of ",
          params[["n"]],
          " rental properties."
        )
      } else if (params[["sampling_method"]] == "stratified") {
        sampling_method = str_c(
          "For each of the 5 main neighborhoods in the city, they get a random sample, and combine their data into a single sample of ",
          params[["n"]],
          " rental properties."
        )
      } else if (params[["sampling_method"]] == "cluster") {
        sampling_method = str_c(
          "They randomly sample 5 streets within the city and collect data on every rental property on the sampled streets. They combine the their data into a single sample of ",
          params[["n"]],
          " rental properties."
        )
      } 
      str_c(
        "An economist is curious about the average cost of rent per month in their large city. ",
        sampling_method,
        " The economist finds that those properties have a mean cost of $",
        params[["xbar"]],
        " per month with a standard deviation of about $",
        params[["s"]],
        ". ",
        " The costs of rent per month for each of the ",
        params[["n"]],
        " properties and the 5-number summary of the dataset is shown below. ",
        question
      )
    }
  ),
  "streaming" = list(
    "procedure" = sample(c("test", "interval"), 1),
    "direction" = "higher",
    "sampling_methods" = c("random", "convenience"),
    "n_params" = c("lower" = 10, "upper" = 50, "sigfigs" = 2),
    "mu0_params" = c("lower" = 1, "upper" = 3, "sigfigs" = 2),
    "mu_params" = c("lower" = 1, "upper" = 3, "sigfigs" = 2),
    "s_params" = c("lower" = 0.2, "upper" = 2, "sigfigs" = 2),
    "text" = function(params) {
      if (params[["procedure"]] == "test") {
        question = str_c(
          "know if the average session length was longer than ",
          params[["mu0"]],
          "."
        )
      } else {
        question = str_c(
          "get a new estimate of the average session length."
        )
      }
      if (params[["sampling_method"]] == "random") {
        sampling_method = str_c(
          " They randomly sampled ",
          params[["n"]],
          " users."
        )
      } else if (params[["sampling_method"]] == "convenience") {
        sampling_method = str_c(
          " They measured the session lengths for the first ",
          params[["n"]],
          " users who logged on to the new site."
        )
      }
      str_c(
        "A website streams movies and television shows to its subscribers. Employees know that the average time a user spends per session on their website is usually ",
        params[["mu0"]],
        " hours. But recently, the website changed its design, and they wanted to ",
        question,
        sampling_method,
        " The session lengths of each of these ",
        params[["n"]],
        " users and the 5-number summary of the data are shown below.",
        " Users in the sample had a mean session length of ",
        params[["xbar"]],
        " hours and a standard deviation of ",
        params[["s"]],
        " hours."
      )
    }
  )
)
```

```{r}
generate_mean_story = function (story) {
  procedure = story[["procedure"]]
  
  # sample size
  n = sample_from_range(story[["n_params"]])
  
  direction = story[["direction"]]
  
  # test
  mu0 = sample_from_range(story[["mu0_params"]])
  s = sample_from_range(story[["s_params"]])
  if (procedure == "test") {
    
    if (sample(1:2, 1) == 1) {
      mu_params = story[["mu_params"]]
      if (direction == "lower") {
        mu_params[["upper"]] = mu0
      } else if (direction == "upper") {
        mu_params[["lower"]] = mu0
      }
      mu = sample_from_range(mu_params)
    } else {
      mu = mu0
    }
    x = sample_x(
      sampling_function = function() {
        x = round(rnorm(n, mu, s))
        xbar = siground(mean(x), 3)
        list("x" = x, "xbar" = xbar)
      },
      direction,
      "xbar",
      mu0
    )[["x"]]
    xbar = round(mean(x), 1)
  } else {
    mu = sample_from_range(story[["mu_params"]])
    x = round(rnorm(n, mu, s))
    xbar = round(mean(x), 1)
  }
  
  confidence_level = sample(c(80, 85, 90, 95, 99), 1)
  alpha = 1 - confidence_level/100
  
  sampling_method = sample(story[["sampling_methods"]], 1)
  
  df = tibble(rent = sort(x))
  summary_table = df %>% 
    summarise(
      min = round(min(rent), 1),
      q1 = round(quantile(rent, 0.25), 1),
      median = round(median(rent), 1),
      q3 = round(quantile(rent, 0.25), 1),
      max = round(max(rent), 1)
    )
  
  list(
    "text" = story[["text"]](
      list(
        "mu0" = mu0,
        "n" = n,
        "xbar" = xbar,
        "s" = s,
        "procedure" = procedure,
        "direction" = direction,
        "sampling_method" = sampling_method,
        "alpha" = alpha,
        "confidence_level" = confidence_level
      )
    ),
    "data" = df,
    "summary" = summary_table
  )
}
```

## Inference for a slope

```{r}
# slope_stories = list()
# generate_slope_story = function (story) {}
```

## Inference for a difference of proportions

```{r}
# diffprop_stories = list()
# generate_diffprop_story = function (story) {}
```

## Inference for a differene of means

```{r}
# diffmean_stories = list()
# generate_diffmean_story = function (story) {}
```

## Inference for a mean difference

```{r}
# meandiff_stories = list()
# generate_meandiff_story = function (story) {}
```

## Chi-squared

```{r}
# chisquared_stories = list()
# generate_chisquared_story = function (story) {}
```

# Random Quiz Question

```{r}
# 1 - proportion (test)
# 4 - mean (interval)
# 9 - mean (test)
# 
set.seed(1)

story_structure = sample(possible_story_structures, 1)
if (story_structure == "proportion") {
  story = sample(proportion_stories, 1)[[1]]
  story_text = generate_proportion_story(story)
} else if (story_structure == "mean") {
  story = sample(mean_stories, 1)[[1]]
  story_text = generate_mean_story(story)
# } else if (story_structure == "slope") {
#   story = sample(slope_stories, 1)[[1]]
#   story_text = generate_slope_story(story)
# } else if (story_structure == "difference of proportions") {
#   story = sample(diffprop_stories, 1)[[1]]
#   story_text = generate_diffprop_story(story)
# } else if (story_structure == "difference of means") {
#   story = sample(diffmean_stories, 1)[[1]]
#   story_text = generate_diffmean_story(story)
# } else if (story_structure == "mean difference") {
#   story = sample(meandiff_stories, 1)[[1]]
#   story_text = generate_meandiff_story(story)
# } else if (story_structure == "chisquared") {
#   story = sample(chisquared_stories, 1)[[1]]
#   story_text = generate_chisquared_story(story)
}
# story_structure
# story_text[["text"]]
```

`r story_text[["text"]]`

```{r}
if (story_structure == "mean") {
knitr::kable(story_text[["data"]], label = "Data")
knitr::kable(story_text[["summary"]], label = "5-number summary")
}
```


## Part 1: Identify the study design

The individuals in this study are: 

How many variables are there and what is/are the variable type(s)?
(Check one box and fill out the question below it.)

* [ ] There is one variable in the study.
    * Variable _________ is (categorical / quantitative)
* [ ] There are two variables in the study.
    * Variable _________ is (categorical / quantitative)
    * Variable _________ is (categorical / quantitative)

The sample is: __________

The population of interest is: ________

What statistical analysis could you use to address the research question? _____________

## Part 2: Represent the data

Draw an appropriate graph of the sample data.

`r if (story_structure %in% c("mean", "difference of means", "mean difference")) {"Describe the distribution."}`
`r if (story_structure %in% c("slope")) {"Describe the relationship."}`

## Part 3: Critique the study design

Are the conditions for the appropriate statistical inference procedure met? If NOT, what improvements could you make to the study design?

## Part 4: Do the statistical analysis

Assume that the conditions are met (even if you showed in the previous section that they are not).

State your conclusion in context, assuming conditions are met and the study design is good.

## Part 5: How much do you trust the conclusion, given the actual study design?






```{r}
# set.seed(1)
# n_vars = sample(c(1, 2), 1)
# var_type = sample(c("categorical", "quantitative"), 1)
# if (n_vars == 1) {
#   if (var_type == "categorical") {
#     n_groups = sample(1:5, 1)
#   }
#   n_groups = sample(c(1, 2), 1)
# } else {
#   n_groups = 1
# }
# data_type = str_c(n_vars, " variable ", var_type, " data (", n_groups, " group)")
# data_type
# if (data_type == "1 variable quantitative data (1 group)") {
#   print("1 var quant (1)")
#   mu = 1 #TODO
#   sigma = #TODO
#   mu0 = 1 #TODO
#   n = 10 #TODO
#   distribution_type = rnorm #TODO
#   x = distribution_type(n, mu, sigma)
#   print(x)
# } else if (data_type == "1 variable categorical data (1 group)") {
#   print("1 var cat (1)")
#   ncats = sample(2:6, 1)
#   concentrations = rep(1, ncats) #TODO
#   probs = rdirichlet(1, concentrations)
#   probs0 = c(rep(1, ncats)) #TODO
#   n = 10 #TODO
#   x = rmultinom(1, n, probs)
#   print(x)
# }  else if (data_type == "1 variable categorical data (2 group)") {
#   print("1 var cat (2)")
#   ncats = 2#sample(2:6, 1)
#   concentrations = rep(1, ncats) #TODO
#   probs1 = rdirichlet(1, concentrations)
#   probs2 = rdirichlet(1, concentrations)
#   # probs0 = c(rep(1, ncats)) #TODO
#   n1 = 10 #TODO
#   n2 = 10 #TODO
#   x1 = rmultinom(1, n1, probs1) #TODO
#   x2 = rmultinom(1, n2, probs1) #TODO
#   print(x1)
#   print(x2)
# }else if (data_type == "1 variable quantitative data (2 group)") {
#   print("1 var quant (2)")
#   mu1 = 1 #TODO
#   mu2 = 1 #TODO
#   sigma1 = 1 #TODO
#   sigma2 = 1 #TODO
#   n1 = 10 #TODO
#   n2 = 10 #TODO
#   distribution_type = rnorm #TODO
#   x1 = distribution_type(n1, mu1, sigma1)
#   print(x1)
#   x2 = distribution_type(n2, mu2, sigma2)
#   print(x2)
# } else if (data_type == "2 variable categorical data (1 group)") {
#   
# }

```

```{r}
# sample_data_type = function(i = NA, allow_chisq = FALSE) {
#   var_type =
#     sample(
#       c("categorical", "quantitative"),
#       1,
#       prob = c(1, 2)
#     )
#   if (allow_chisq || var_type == "quantitative") {
#     n_vars = sample(c(1,2), 1, prob = c(2, 1))
#   } else {
#     n_vars = 1
#   }
#   if (n_vars == 1) {
#     if (var_type == "categorical") {
#       if (allow_chisq) {
#         n_groups = sample(1:5, 1, prob = c(5, 5, 1, 1, 1))
#       } else {
#         n_groups = sample(1:2, 1)
#       }
#     } else if (var_type == "quantitative") {
#       n_groups = sample(1:2, 1)
#     }
#   } else {
#     n_groups = 1
#   }
#   data_type =
#     str_c(
#       n_vars,
#       " variable ",
#       var_type,
#       " data (",
#       n_groups,
#       " group)"
#     )
#   data_type
# }
```

```{r}
# ggplot(NULL, aes(x = sapply(1:10000, sample_data_type, allow_chisq = TRUE))) +
#   geom_bar() +
#   coord_flip()
```
